---
title: "Anova in R"
output: html_notebook
---

# An overview of running ANOVA in R

For this analysis we will be doing a mixed anova. It has 2 between variables (condition: facebook, no facebook) and three within conditions (timepoint: t1, t2, t3). The data is taken from Vanman, Tobin, and Baker (2018). The journal article can be found [here](https://www.tandfonline.com/doi/abs/10.1080/00224545.2018.1453467?journalCode=vsoc20) and the OSF page can be found [here](https://www.tandfonline.com/doi/abs/10.1080/00224545.2018.1453467?journalCode=vsoc20).  

# Analysis using R markdwon 

A good [reference guide for RMarkdown](https://rmd4sci.njtierney.com/) has been written by [Nick Tierney] (https://www.njtierney.com/) 

## Set options 

```{r setup , include=TRUE}
knitr::opts_chunk$set(echo = TRUE, 
                      fig.align = "center",
                      fig.width = 4, 
                      fig.height = 4, 
                      dev = "png",
                      cache = TRUE, 
                      message = FALSE)
```

# install packages

For the anova analysis we will need the pacakges `afex`, `tidyverse`, and, `apa`.
```{r library}
library(tidyverse)
library(afex)
library(apa)
```

# Load data

The data have already been cleaned. For this analysis we are only going to look at the three timepoints of cortisol and their differences across the two facebook groups. 

