---
title: "Linear regression and mediation"
output: html_notebook
---

# An overview of running linear regression and mediation in R

For this analysis we will be doing heirachial linear models and mediation analyses. The data we are using comes from Larwood (unpublished) and the data can be found [here](https://raw.githubusercontent.com/joellarwood/MusicEmoRegInRumination/master/data/s2Processed.csv). The cleaning of the data can be seen in the r script `cleaning_larwood_2017.R` which is in the `script` subfolder. We will also be using data from Larwood, Vanman, and Dingle (2020). The data for this project has also been cleaned, this time using the script `cleaning_larwood_2020.R` in the `script` folder. The paper for this data can be found [here]() and the OSF page [here]()

# Analysis using R markdwon 

A good [reference guide for RMarkdown](https://rmd4sci.njtierney.com/) has been written by [Nick Tierney] (https://www.njtierney.com/) 

## Set options 
Th
```{r setup , include=TRUE}
knitr::opts_chunk$set(echo = TRUE, 
                      fig.align = "center",
                      fig.width = 4, 
                      fig.height = 4, 
                      dev = "png",
                      cache = TRUE, 
                      message = FALSE)
```

# install packages

For the anova analysis we will need the pacakges `sjPlot`, `tidyverse`, and, `lavaan`.
```{r library}
library(tidyverse)
library(sjPlot)
library(lavaan)
```

## Mediation 

### Lavaan 

The `lavaan` (latent variable analysis) package gives a set of functions to perform linear models including CFA, LGM, SEM, and mediation. We are just going to do mediation and an tutorial can be found on the [`lavaan` webpage](http://lavaan.ugent.be/tutorial/mediation.html)

